Renewal and stability in populations structured by remaining years of life

### 2015-11-10 ThanoRepro/ThanoReproMPIDR.tex
MPIDR version committed. This has been submitted to post as a working paper while under review at DR

\title{Renewal and stability in populations structured by remaining years of
life}
\author{(author redacted)}
\maketitle

%\ackn{Research
%reported in this manuscript was supported by the U.S.
%National Institute On Aging of the National Institutes of Health under award
% numbers R01-AG011552 and R01-AG040245. The content is solely the responsibility of the author and does not necessarily represent the official views of the funding
%agency.}

\section*{Structured abstract}

>>>>

\title{Renewal and stability in populations structured by remaining years of
life}
\author{Tim Riffe \\ Max Planck Institute for Demographic Research}
\maketitle

\vspace{8cm}
\ackn{Research
reported in this manuscript was supported by the U.S.
National Institute On Aging of the National Institutes of Health under award
 numbers R01-AG011552 and R01-AG040245. The content is solely the responsibility of the author and does not necessarily represent the official views of the funding
agency.}

\pagebreak
\section*{Structured abstract}
